Report for the Deep Learning Course Assignment 2

### 2016-12-11 practical_3/report/report_methenitis.tex
visualization done
Visualization for siamese

\author{
  David S.~Hippocampus \\
  \texttt{hippo@cs.cranberry-lemon.edu}
}

@@

>>>>

\author{
  Georgios Methenitis \\
  \texttt{georgios.methenitis@cwi.nl}
}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.4\textwidth]{visualization-linear-features_flatten.pdf}\\	
\includegraphics[width=0.49\textwidth]{visualization-linear-features_fc1.pdf}\	
\includegraphics[width=0.49\textwidth]{visualization-linear-features_fc2.pdf}
\caption{Visualization of the features in the 2-d space of the \texttt{flatten} layer (top), \texttt{fc1} (bottom-left), \texttt{fc2} (bottom-right).}
\label{fig:5}
\end{figure}
